The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-06-05 article.tex
Updates from ShareLaTeX
Improve wording

Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as the known clock model prior in the Bayesian inference.

@@

We produce two data sets as a comma-separated file.
Each parameter combination has ten replicates.

We set the number of replicates for each parameter combination such,
that this file and a possible copy can be handled in R's memory.
Each row will then contain a parameter set and the generated nLTT 
statistics (see \ref{table:specs} for the exact data specification).
The above-mentioned memory constraints allows for $2 \cdot 10^3$ rows. 
With 87 \textbf{[NOTE: volatile value, recalculate]} combinations of biological parameter, there will be 
168 \textbf{[NOTE: volatile value, recalculate]} replicates per parameter set.

>>>>

Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as one of the two clock models assumed in the Bayesian inference.

@@

We produce two data sets as a comma-separated file.
Each parameter combination has ten replicates.
We set the number of replicates for each parameter combination such,
that this file and a possible copy can be handled in R's memory.
Each row will then contain a parameter set and the generated nLTT 
statistics (see \ref{table:specs} for the exact data specification).
The above-mentioned memory constraints allows for $2 \cdot 10^3$ rows. 
With 87 \textbf{[NOTE: volatile value, recalculate]} combinations of biological parameter, there will be 
168 \textbf{[NOTE: volatile value, recalculate]} replicates per parameter set.
